Efficient Parallelization of Sparse Representation for Face Recognition

### 2010-10-20 paper/main.tex
Fleshing out the outline...

\begin{abstract}
   The ABSTRACT is to be in fully-justified italicized text, at the top
   of the left-hand column, below the author and affiliation
   information. Use the word ``Abstract'' as the title, in 12-point
   Times, boldface type, centered relative to the column, initially
   capitalized. The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous CVPR abstracts to get a feel for style and length.
\end{abstract}

@@

\section{Characteristics of the ALM Algorithm}
Describe the two variants of the ALM algorithm
Show Pseudocode for one variant
\subsection{Computational Complexity}

@@

{\small
\bibliographystyle{ieee}
\bibliography{faces}
}

>>>>

\begin{abstract}
Abstract
\end{abstract}

@@

\cite{Wagner2009-CVPR}
\cite{Wright2009-PAMI}

\section{Characteristics of the ALM Algorithm}
Describe the two variants of the ALM algorithm
Show Pseudocode for one variant
\subsection{Computational Complexity}
The Matrix-vector computions are O($mn$), and the vector-vector operations are O($m$), 
in terms of both computation cost and memory-bandwidth.
Therefore, assuming the iterative solver always takes a constant number of iterations,
the computational complexity of the overall algorithm is linear in the problem size.

@@

{\small
\bibliographystyle{../authorkit/ieee}
\bibliography{faces}
}
